Software Developers and Computers as Social Actors

### 2016-04-25 paper/draft1.tex
Updates from ShareLaTeX

We recreated Nass's intelligent tutor using the details found in the original paper. Our experiment has two independent variables to test the two research questions:\\
\begin{enumerate*}
    \item{\emph{Evaluation method: Participants either used one computer for the entire experiment, or they completed the Evaluation Session on an identical pen-and-paper questionnaire.}}
\end{enumerate*}

\begin{comment}
\begin{enumerate}
    \item {\textit{Evaluation method}: Participants either used one computer for the entire experiment, or they completed the final evaluation on an identical pen-and-paper questionnaire.}
    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
\end{enumerate}
\end{comment}

>>>>

We recreated Nass's intelligent tutor using the details found in the original paper. Our experiment has two independent variables to test the two research questions:
\begin{enumerate}
    \item{\emph{Evaluation method:} Participants either used one computer for the entire experiment, or they completed the Evaluation Session on an identical pen-and-paper questionnaire.}
    \item {\textit{Computing environment}: Participants either used their personal laptops or a public computer in a computer lab.}
\end{enumerate}

\begin{comment}
\begin{enumerate}
    \item {\textit{Evaluation method}: Participants either used one computer for the entire experiment, or they completed the final evaluation on an identical pen-and-paper questionnaire.}
    \item {\textit{Computing environment}: Participants either used personal laptops or a public computer in a computer lab.}
\end{enumerate}
\end{comment}
